\documentclass{article}
\usepackage{graphicx}
\usepackage{amstext}
\usepackage{enumerate}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{amsmath}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proof}{Proof}[section]
\DeclareMathOperator*{\argmax}{arg\,max}
\usepackage[top=1in,bottom=1in,left=1.25in,right=1.25in]{geometry}
\title{Broadcast 1}
\author{Alex Chen}

\begin{document}
\maketitle
\abstract
Let $N$ be a finite set and $z$ be a real-valued function defined on the set of subsets of $N$ that satisfied \begin{displaymath}
z(S)+z(T)\geq z(S\cup T)+z(S\cap T), \forall S,T \subseteq N
\end{displaymath}. Such a function is called submodular. We consider the problem  \begin{displaymath} \max_{S\subseteq N} \{ z(S):|S|\leq K, \text{z(S) is submodular} \} \end{displaymath}.
\par The problem of finding a maximum weight independent set in a matroid, when the elements of the matroid are colored and the elements of the independent set can have no more than K colors, can be posed in this framework.
\par Then we analyze the greedy heuristic for submodular set functions, when z(S) is nondecreasing and $z(\emptyset)=0$, the greedy heuristic always produces a solution whose value is at least  $1-[(K-1)/K]^K$ times the optimal value. This bound can be achieved for each K and has a limiting value of $(1-1/e)\approx 63\% $

\section{The greedy heuristic for submodular set functions}
\par Here is a submodular problem
\begin{equation}
\max_{S\subseteq N}\{z(S):|S|\leq K,z(S) submoluar.\}
\label{N1}
\end{equation}
\par A natural solution to this problem is to start from the null set and add elements one at a time, taking at each step that element which increases z the most. We define this solution as greedy heuristic formally. we let $ \rho _j(S)=z(S\cup\{j\})- z(S)$

\begin{algorithm}
        \caption{The greedy heuristic}
\begin{algorithmic}[1]
\STATE Initialize a null set $S=\emptyset$ and a finite set $N$ ;\
\STATE Every iteration, add a element to S, $|S|\leq K$       \
\STATE \emph{Iteration} t.\
\WHILE{$ t \leq K $}
    \STATE Select $\max i\in N^{t-1}$
    \STATE For which $\rho_{i}(S^{t-1}) = z(S^{t-1}\cup\{i\})- z(S^{t-1})$
    \STATE Set $\rho_{t-1}=\rho_{i}(S^{t-1})$
\IF{$\rho > 0$}
    \STATE Select$\{i\} \in N^{t-1}$
    \STATE Then update $S^t=S^{t-1}\cup \{i(t)\}$ and $N^t=N^{t-1}-{i(t)}$
\ELSE
    \RETURN $ S^{K^*}, K^*=t-1<K $
\ENDIF
\STATE $t\rightarrow t+1$\
\ENDWHILE $K^*=t=K$
\end{algorithmic}
\end{algorithm}

\par Note that
\begin{equation}
Z^G=Z({S^K}^*)=z(\emptyset)+\rho_0 + ... +\rho_{K^*-1}, K^*\leq K
\label{Z^G}
\end{equation}
\par is the solution generated by greedy heuristic. \par And $z(S)$ is the optimal solution.
\par We have the theorem:
\begin{theorem}
    \begin{equation}
\frac{\text{value of greedy approximation}}{\text{value of optimal solution}}=\frac{Z^G-z(\emptyset)}{Z-z(\emptyset)}\geq 1-{(\frac{K-1}{K})}^K
\label{theorem1}
    \end{equation}
\end{theorem}
\begin{proof}
Before we proof Eq.(\ref{theorem1}), We will proof other equivalence that needed:
\par Let N be a finite set and $\forall A,B \in N $ that satisfy:
\begin{equation}
z(A)+z(B)\geq z(A\cup B)+z(A\cap B)
\label{submod_definition}
\end{equation} The function z defined on the set of subsets of N is called submodular function.
\par Take $A=S\cup \{j\}$ and $B=T$, $S\subseteq T$, $j\notin T$:
\par We have
\begin{equation}
z(S\cup \{j\})+z(T)\geq z(T\cup \{j\})+z(S)
\end{equation}
Or
\begin{equation}
\rho_j(S) \geq \rho_j(T)
\label{rhoST}
\end{equation}
For arbitrary S and T with $T-S = \{j1,...,jr\}$ and $S-T = \{k1,...,kq\}$, we have
\begin{equation}
\begin{split}
    z(S\cup T)-z(S) & = z(S\cup T) - Z(S\cup \{j_1,...,j_{r-1}\}) \\
                    & + Z(S\cup \{j_1,...,j_{r-1}\})- Z(S\cup \{j_1,...,j_{r-2}\}) \\
                    & + ... - ... \\
                    & + Z(S\cup \{j_1,j_2\}) - Z(S\cup \{j_1\}) \\
                    & + Z(S\cup \{j_1\}) - Z(S) \\
                    & = \sum_{t=1}^{r}\rho_{j_t}(S\cup \{j_1,...,j_{t-1}\}) \\
                    & \leq \sum_{t=1}^{r}\rho_{j_t}(S) \\
                    & = \sum_{j\in T-S}\rho_{j}(S)
\end{split}
\label{7}
\end{equation}
Similarly:
\begin{equation}
\begin{split}
    z(S\cup T)-z(T)& =\sum_{t=1}^{q}\rho_{k_t}(T\cup \{k_1,...,k_{t-1}\})\\
                    & =\sum_{t=1}^{q}\rho_{k_t}(T\cup \{k_1,...,k_{t}\}-\{k_t\})\\
                    & \geq \sum_{t=1}^{q}\rho_{k_t}(T\cup S-\{k_t\})\\
                    & = \sum_{j\in S-T}\rho_{j}(S\cup T - \{j\})
\end{split}
\label{8}
\end{equation}
With Eq.(\ref{7}) and (\ref{8})
\begin{equation}
z(T)\leq z(S)+\sum_{j\in T-S}\rho_j(S)-\sum_{j\in S-T}\rho_j(S\cup T -\{j\} ), \forall S,T \subseteq E
\label{9}
\end{equation}
\par If z is a submodular set function on E with $-\theta\leq \rho_j(S)\leq \psi, \forall S\subseteq E, j\in E-S$, then:
\begin{equation}
z(T)\leq z(S)+\sum_{j\in T-S}\rho_j(S)+|S-T|\theta
\label{eq233}
\end{equation}
\par Taking $T$ to be an optimal solution, $S$ to be the set $S^t$ which is generated after t iterations of the algorithm[1]. Using Eq. (\ref{eq233})
$$ Z=z(T), \rho_j(S^t)\leq\rho_t, \rho_t\geq 0,$$
$$|S^t-T|\leq t, \theta \geq 0, |T-S^t|\leq K, t\leq K$$
and $$z(S^t)=z(\emptyset)+\sum_{i=0}^{t-1}\rho_i$$
we obtain
\begin{equation}
\begin{split}
    Z & \leq z(S^t)+K\rho_t + t\theta \\
    & =z(\emptyset)+\sum_{i=0}^{t-1}\rho_i+K\rho_t + t\theta
\end{split}
\end{equation}
when t=0, we obtain $Z-z(\emptyset)\leq K\rho_0 \leq K(Z^{G_0}-z(\emptyset))$, therefore
\begin{equation}
\frac{Z-Z^{G_0}}{Z-z(\emptyset)}\leq \frac{K-1}{K}
\end{equation}
when $\theta=0$,
\begin{equation}
\begin{split}
Z-z(\emptyset)&\leq \sum_{i=0}^{t-1} \rho_i+K \rho_t \\
              & = \rho_0 + ... + \rho_{t-1} + K \rho_t \\
              & Eq. (\ref{Z^G}) \\
              & = Z^{G_{t+1}} - z(\emptyset) + (K-1)\rho_t \\
              & = Z^{G_{t+1}} - z(\emptyset) + (K-1)({Z^{G_{t+1}}-Z^{G_t}})
\end{split}
\end{equation}
We obtain
$$\frac{Z-Z^{G_{t+1}}}{Z-Z^{G_t}}\leq \frac{K-1}{K}$$
\begin{equation}
\begin{split}
\frac{Z-Z^G}{Z-z(\emptyset)}& = \frac{Z-Z^{G_K}}{Z-Z^{G_{K-1}}}\frac{Z-Z^{G_{K-1}}}{Z-Z^{G_{K-2}}}...\frac{Z-Z^{G_t}}{Z-Z^{G_{t-1}}}...\frac{Z-Z^{G_0}}{Z-Z(\emptyset)} \\
                            &\leq {(\frac{K-1}{K})}^K
\end{split}
\end{equation}
so we have
\begin{equation}
\frac{\text{value of greedy approximation}}{\text{value of optimal solution}}=\frac{Z^G-z(\emptyset)}{Z-z(\emptyset)}\geq 1-{(\frac{K-1}{K})}^K \geq 1-\frac{1}{e} \approx 63\%
\end{equation}
\end{proof}

\begin{appendix}

\end{appendix}

\end{document}
